---
output: 
  pdf_document:
    keep_tex: true
    fig_caption: yes
    latex_engine: pdflatex
    template: ./syllabus.tex
geometry: margin=1in

title: "CIS 338: Content Management Systemss"
author: Nate LaClaire
date: "Spring 2022"

email: "nathaniel.laclaire@maine.edu"
web: "natelaclaire.dev"
officehours: "By Appointment"
office: "202 Katz"
classroom: "*online*"
classhours: "Asynchronous"

fontfamily: mathpazo
fontsize: 11pt
header-includes:
   - \linespread{1.05}
---

```{r setup, include=FALSE, cache=F, message=F, warning=F, results="hide"}
knitr::opts_chunk$set(cache=TRUE)
knitr::opts_chunk$set(fig.path='figs/')
knitr::opts_chunk$set(cache.path='_cache/')
knitr::opts_chunk$set(warning=F, message=F)
# knitr::opts_knit$get(kable.force.latex = TRUE)
```



```{r dates_bib, include=FALSE}
knitr::opts_chunk$set(cache=FALSE, dev='pdf')
mon <- as.Date("2022-01-18")
# fri <- as.Date("2016-01-08")

advdate <- function(obj, adv) {
 tmon <- obj + 7*(adv-1)
 tfri <- obj + 4 + 7*(adv-1)
 tmon <- format(tmon, format="%m/%d")
 tfri <- format(tfri, format="%m/%d")
 zadv <- sprintf("%02d", adv)
 tmp <- paste("Week ",zadv,sep='',", ", tmon," - ",tfri)
 return(tmp)
}

library(RefManageR)
# library(knitcitations)
# library(rcrossref)
bib <- ReadBib("master.bib")
myopts <- BibOptions(bib.style = "authoryear", style="latex", first.inits=FALSE, max.names = 20)

```

# Required Text and Materials

None

# Required Software

Students will be required to install an SSH and an SFTP client. Free options will be shared in the first class.

# Course Objectives

This course will introduce students to concepts used in modern Content Management Systems (CMS), specifically applying these concepts using the WordPress CMS. This will include:

-	Role of content management technologies to design, edit, manage and publish Web content
-	Implementing common Web site features using a CMS
-	Open-source Web technologies
-	Overview of WordPress

Expect to work an average of six to nine hours a week on homework assignments, discussion assignments, and studying. This may vary on any particular week depending on class workload.

# Learning Outcomes

Upon completion of this course, the student should be able to:

-	Create and install a database
-	Download, install and configure WordPress
-	Back up WordPress files and database
-	Explore and plan a site with storyboard
-	Add WordPress plugins 
-	Create pages
-	Create posts
-	Add content to pages
-	Add tags and categories
-	Moderate comments
-	Change WordPress themes and create child themes
-	Work with WordPress blocks and menus
-	Modify CSS files
-	Set WordPress user roles
-	Create a Contact form with CAPTCHA in WordPress
-	Configure an image slider and gallery
-	Insert drop-down menus
-	Install security updates
-	Transfer site to new server

# Electronic Learning Tools

Participation in this course requires that you have access to high speed internet. This is especially critical for accessing online resources.

*Brightspace®* is a content management system that provides the interactive interface for students to access course materials, communicate with instructors and other students, and to upload homework assignments. The Brightspace® site includes the syllabus as well as other course materials. If you have technical issues with Brightspace, please contact our IT helpdesk at UMAHelp@maine.edu or 621-3475.

# Student Responsibilities

Students are responsible for watching and reading the assigned material available in Brightspace, performing the activities in the video tutorial, and submitting Homework Assignments and Discussion Assignments on or before the due date.

Students may upload late homework assignments and discussion assignments for two weeks with

*a ten (10) -point deduction for each week*

After two weeks, the homework/discussion assignment will no longer be accepted and a grade of "0" will be posted to the gradebook.

Graded assignments are due on Saturday at midnight of the week they are assigned. Assignments are graded on the following Sunday or Monday. Students should review feedback before starting the next assignment.

# Course Outline

To maximize your learning experience, you should:

-	Watch the videos, complete the tutorial using the Tutorial Site along with the instructor, and review any supplementary materials available in Brightspace.
-	Communicate with the instructor if there is a concept that you do not understand.
-	Complete discussion assignments on or before the due date.
-	Complete the homework assignment using the Portfolio Site and indicate that you have completed it through the Course Content tab in Brightspace on or before the due date.

## `r advdate(mon, 2)`: The First Topic Where We Read John Vasquez

```{r, echo = FALSE, results="asis"} 
bib[author = "vasquez"]
``` 

##  `r advdate(mon, 3)`: Read the Nos. 90-97 Items in My Bib

```{r, echo = FALSE, results="asis", eval=F} 
bib[90:97]
``` 

*Your "Slow Ride" appreciation paper is due in Thursday's class*.

##  `r advdate(mon, 4)`: Read Bib Item No. 120

```{r, echo = FALSE, results="asis", eval=F} 
bib[120]
``` 



##  `r advdate(mon, 5)`: The Fourth Topic with Bib Item No. 510

```{r, echo = FALSE, results="asis", eval=F} 
bib[510]
``` 

##  `r advdate(mon, 6)`: Keep
##  `r advdate(mon, 7)`: Going
##  `r advdate(mon, 8)`: Down

##  `r advdate(mon, 9)`: the

##  `r advdate(mon, 10)`: Line

##  `r advdate(mon, 11)`: Until

##  `r advdate(mon, 12)`: You

## `r advdate(mon, 13)`: Are

##  `r advdate(mon, 14)`: Done

##  `r advdate(mon, 15)`: with


##  `r advdate(mon, 16)`: your


##  `r advdate(mon, 17)`: Syllabus 

# Grading Criteria

- **80%** of your grade will be determined by Homework Assignments.

- **20%** of your grade will be determined by Discussion Assignments.

A 94-100%, A- 90-93%, B+ 87-89%, B 83-86%, B- 80-82%, C+ 77-79%, C 73-76%, C- 70-72%, D+ 67-69%, D 63-66%, D- 60-62%, F below 60%.

# Communication

Students are encouraged to ask questions or make comments and/or suggestions. This helps you reinforce your learning and maximize your learning experience. The Brightspace® content management system is available for student chat discussions, email communication, and to view course announcements at https://courses.maine.edu/d2l/home

For purposes of this class, communication is defined as interactively engaging with the Brightspace® system, contacting the instructor via email or phone if you have questions outside of class, and responding to the instructor's emails or phone calls.

# Academic Integrity

Cheating on an assignment or assessment will result in a grade of "0." Repeated offenses will result in a grade of "F" for the semester. Cheating includes uploading another student's work as your own, copying another student's work, or asking someone else to complete the assessment for you. Students should familiarize themselves with UMA's policies and procedures regarding Academic Integrity at
http://www.uma.edu/studenthandbookpol-s.html#saic

# Class Withdrawals

Before withdrawing from a class, students are encouraged to contact the instructor. The instructor may be able to offer an alternative to dropping the class. Ultimately, if a student finds it necessary to withdraw from a class, students must follow school policy. Students who just stop attending a class, but who have not officially withdrawn, will receive a grade based on work completed up until the last date of attendance. Most often, this results in a failing grade. *Students are not automatically withdrawn from a class.*

L Grade: The grade of "L" is awarded if you stop attending, but do not withdraw from the course. The "L" grade is computed into the grade point average as a failing grade.

W Grade: The grade of "W", withdraw, is posted if you drop the course during the first 60% of the semester. A "W" grade is not computed into the grade point average. After the 60% point, the grade of WF may be assigned.

WF Grade: The "WF" grade is awarded when a course is dropped after 60% of the term is completed and depends upon your performance up to that point. If you are passing the course the grade of "W" is awarded. If you are failing the course at the time of withdrawal the grade of "WF", withdraw failing, may be assigned. A "WF" is computed into the grade point average as a failing grade.

# Incompletes

Awarding of the grade of Incomplete is at the discretion of the instructor. An Incomplete is a temporary grade indicating that specific arrangements have been made with the instructor to complete work by a later date not to exceed 210 days after the end of the term. Incomplete grades will be granted only under unusual circumstances which prevent a student from completing the course during the semester in which the student is enrolled. The student must request the grade of incomplete from the instructor prior to the end of the semester. Not all requests will be approved. Incompletes must be completed within 210 days of the end of the semester or by a specified time that is jointly agreed upon by the instructor and student. Otherwise, the grade will revert to an "F" after 210 days from the end of the semester. Any extension beyond that requires the Dean's approval.

# Accommodations for Students with Disabilities

If you have a disability which may affect your ability to participate fully in this course, it is your responsibility to request accommodations promptly. Contact the Department of Learning Success on your campus, or Coordinator of Student Services at your University College Center to discuss possible assistance. Accommodations must be requested each semester, and are not provided retroactively. More information can be found at: http://www.uma.edu/academics/student-support/student- development/disability-services/

# Title IX

The University of Maine at Augusta is committed to providing an environment free of violence and harassment based on sex and gender. Such civil rights offences are subject to the same accountability and support as offences based on race, national origin, etc. If you or someone else within the UMA community is struggling with sex discrimination, sexual harassment, sexual assault relationship violence, or stalking you can find the appropriate resources at: https://www.uma.edu/titleixinfo.html.

\newpage


# Recommended Readings

```{r, echo = FALSE, results="asis"} 
bib["vasquez2009twp", "wagner2007ws"]
``` 